Cybersecurity Education Is Too Important\\To Be Left To The Specialists

### 2019-06-22 FIE2019-final-TPJHD.tex
Tweaks to abstract

\begin{abstract}
% submitted abstract (100-500 word limit):
There are numerous dimensions to cybersecurity education: from theory to practice, hardware and software, to social and politics/policy (as well as other important facets). A multitude of national and international model curricula and recommendations have been presented and discussed in recent years, with varying levels of impact on education and practice. This paper address the key questions: ``What cybersecurity is taught and what cybersecurity should be taught to general computer science students?'' , ``Should cybersecurity be taught stand-alone or in an integrated manner to general Computer Science students?'' and ``Can accreditation by professional, statutory and regulatory bodies enhance the provision of cybersecurity within a body's jurisdiction?''.

>>>>

\begin{abstract}
% submitted abstract (100-500 word limit):
There are numerous dimensions to cybersecurity education: hardware and software, from theory to practice (and vice versa), to social and politics/policy (as well as other important facets). A multitude of national and international model curricula and recommendations have been presented and discussed in recent years, with varying levels of impact on education, policy and practice. This paper address the key questions: ``What cybersecurity is taught and what cybersecurity should be taught to general computer science students?'' , ``Should cybersecurity be taught stand-alone or in an integrated manner to general Computer Science students?'' and ``Can accreditation by professional, statutory and regulatory bodies enhance the provision of cybersecurity within a body's jurisdiction?''.
